A Philosophy of (Inductive) Testing

### 2024-03-08 mss.tex
Finalize
Adapt for HTML.

We were intentionally dismissive of testing methodologies above because they are mere conventions. There is however some actual theory we can leverage in figuring out what and how to test.\footnote{\citet{WikipediaInduction} provides a modestly technical exposition of mathematical induction. You can skip it because we will explain it non-rigorously for lay programmers. We also quibble about the inclusion of zero as a natural number. While old school maths started the natural numbers with "1", but computer science has since infected maths. Have you ever seen zero of anything? No, it is not natural at all. Zero is a very, very special number.2 It's an abstraction that does not map to anything in the physical world.}

@@

\begin{enumerate}
  \item  Strive to make the collection of units of testing exhaustive, both primitive units of code and units of work from the user perspective.
  \item  Test inductively wherever possible.
  \item  Test from a white or gray box perspective.
  \item  Test the failure modes.
  \item  Test all the examples in your documentation.
  \item  In a world lacking documentation tests may be the only real specification.\footnote{Cf. the definition by \citeauthor[p. xvi]{Feathers2005} that “legacy code is simply code without tests.”  The entire text may thus be commended as a thorough guide to testing despite its name.}
  \item  Regression tests are the key to refactoring with confidence. Beautiful code comes from refactoring.
\end{enumerate}

>>>>

We were intentionally dismissive of testing methodologies above because they are mere conventions. There is however some actual theory we can leverage in figuring out what and how to test.\footnote{\citet{WikipediaInduction} provides a modestly technical exposition of mathematical induction. You can skip it because we will explain it non-rigorously for lay programmers. We also quibble about the inclusion of zero as a natural number. While old school maths started the natural numbers with “1”, but computer science has since infected maths. Have you ever seen zero of anything? No—it is not natural at all. Zero is a very, very special number. It's an abstraction that does not map to anything in the physical world.}

@@

\begin{enumerate}
  \item  Strive to make the collection of units of testing exhaustive, both primitive units of code and units of work from the user perspective.
  \item  Test inductively wherever possible.
  \item  Test from a white or gray box perspective.
  \item  Test the failure modes.
  \item  Test all the examples in your documentation.
  \item  In a world lacking documentation tests may be the only real specification.\footnote{Cf. the definition by \citeauthor[p. xvi]{Feathers2005} that “legacy code is simply code without tests.”  The entire text may thus be commended as a thorough guide to testing despite its name.}
  \item  Regression tests are the key to refactoring with confidence. Beautiful code comes from refactoring.  \tombstone{}
\end{enumerate}
